%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\usepackage[style=numeric, backend=biber]{biblatex}
\addbibresource{bibliography.bib}

\begin{document}
\header{Benjamin }{MOREAU}
       {PhD Student}


% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    3 Chemin de bonneville
    44300 Nantes
    France
    ~
    (+33) 6 98 74 86 06
    ~
    \href{mailto:benjamin.moreau1@univ-nantes.fr}{benjamin.moreau1
    @univ-nantes.fr}
    ~
    \href{mailto:benjamin.moreau@opendatasoft.com}{benjamin.moreau
    @opendatasoft.com}
    ~
    \href{https://github.com/benjimor}{github.com/benjimor}
  \section{Languages}
    Native language: French
    Professional level: English
    Notions: Spanish
  \section{Programming}
  	Python, Java, C++, C
  \section{Web Technologies}
 	Django, Spring, Node JS, 
 	PHP, CSS3 \& HTML5,
 	Javascript,
 	AngularJS, VueJS
  \section{Semantic Web}
  	RDF, OWL, SPARQL, RML,
  	Triple Pattern Fragments
  \section{Version Control}
  	Git, Subversion
  \section{Databases}
  	MySQL, CouchDB,
  	Elastic Search, Neo4j
  \section{Word Processing}
  	\LaTeX, Microsoft Word
\end{aside}

\section{Interests}

Semantic Web, Web of Data, Data Privacy, Data Integration

\section{Education}

\begin{entrylist}
  \entry
    {since 2017}
    {Ph.D. Student}
    {LS2N \& OpenDataSoft, Nantes}
    {\emph{Computer Sciences}\\
    \emph{Supervisors: Pr. Pascal Molli, Patricia Serrano Alvarado, Emmanuel Desmontils}}
  \entry
    {2015–2017}
    {Master’s degree}
    {University of Nantes, Nantes, France}
    {Software Engineering and Distributed Architectures}
  \entry
    {2012–2015}
    {Bachelor’s degree}
    {University of Nantes, Nantes, France}
    {Computer Sciences}
  \entry
    {2012}
    {French Baccalauréat S. with honors}
    {Lycée Clémenceau, Nantes, France}
    {}
\end{entrylist}

\section{Teaching}

\begin{entrylist}
  \entry
    {01–05 2018}
    {Introduction to Research, University of Nantes, France}
    {Co-supervisor.}
    {\emph{1 First year Master student working on research topics.}}
 \end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {01–06 2017}
    {OpenDataSoft, Paris and LS2N, Nantes}
    {R\&D Internship.}
    {\emph{Introduce semantic web technologies to OpenDataSoft platform.}}
  \entry
    {05–08 2016}
    {Sopra Steria}
    {Internship.}
    {\emph{Development of a web application used to monitor web services and applications availability.}}
  \entry
    {04–08 2015}
    {Enedis}
    {Internship.}
    {\emph{Development of several scripts that collect data.}}
\end{entrylist}

\section{Applications}

\begin{entrylist}
  \entry
    {2017}
    {ODMTP: On Demand Mapper with Triple pattern matching\cite{moreau2017querying}}
    {\href{https://github.com/benjimor/odmtp-tpf}{github.com/benjimor/odmtp-tpf}}
    {\emph{A Triple Pattern Fragments server enabling triple pattern matching over non-RDF datasources.}}
\end{entrylist}

\section{Publications}

\nocite{*}
\printbibliography[sorting=chronological, heading=subbibliography, heading=none]

\end{document}